Software Citation Principles

### 2016-04-05 sc-principles/software-citation-principles.tex
further formatting changes in Section 3.

We have documented and analyzed a set of use cases related to software citation
in \cite{SC-Use-Cases}. Table~\ref{tab:use_cases} summarizes these use cases and
makes clear what the requirements are for software citation in each case. In the following list,
we clarify a few notions used in the table.
\begin{itemize}

\item ``Researcher'' includes both academic researchers (e.g., postdoc,
tenure-track faculty member) and research software engineers;

\item ``Publisher'' includes both traditional publishers that publish text
and\slash or software papers as well as archives such as Zenodo that directly
publish software;

\item ``Repository'' refers to public software repositories such as Astronomy
Source Code Library (ASCL)~\cite{ascl}, GitHub, Netlib, Comprehensive R Archive
Network (CRAN), institutional repositories;

\item ``Funder'' is a group that funds software or work using software;

\item Examples of ``Indexer'' include Scopus, Web of Science, Google Scholar,
and Microsoft Academic Search;

\item ``Domain group'' includes bioCADDIE~\cite{bioCADDIE}, Computational
Infrastructure for Geodynamics (CIG)~\cite{CIG}, etc.;

\item ``Unique identifier'' refers to identifiers such as a DOI, ARK, or PURL;

\item``reproduce'' can mean reproduction, replication, verification, validation,
repeatability, and\slash or utility.
\end{itemize}

@@

If certain metadata are not available, alternatives may be provided:
\begin{itemize}
\item version number and release date: download date
\item location\slash repository: contact name\slash email if not publicly
  available
\end{itemize}

>>>>

We have documented and analyzed a set of use cases related to software citation
in \cite{SC-Use-Cases}. Table~\ref{tab:use_cases} summarizes these use cases and
makes clear what the requirements are for software citation in each case. In that table,
we use the following definitions:
\begin{itemize}

\item ``Researcher'' includes both academic researchers (e.g., postdoc,
tenure-track faculty member) and research software engineers.

\item ``Publisher'' includes both traditional publishers that publish text
and\slash or software papers as well as archives such as Zenodo that directly
publish software.

\item ``Repository'' refers to public software repositories such as Astronomy
Source Code Library (ASCL)~\cite{ascl}, GitHub, Netlib, Comprehensive R Archive
Network (CRAN), institutional repositories.

\item ``Funder'' is a group that funds software or work using software.

\item ``Indexer'' examples include Scopus, Web of Science, Google Scholar,
and Microsoft Academic Search.

\item ``Domain group'' includes bioCADDIE~\cite{bioCADDIE}, Computational
Infrastructure for Geodynamics (CIG)~\cite{CIG}, etc..

\item ``Unique identifier'' refers to identifiers such as a DOI, ARK, or PURL.

\item``Reproduce'' can mean reproduction, replication, verification, validation,
repeatability, and\slash or utility.
\end{itemize}

@@

In some cases, if particular metadata are not available, alternatives may be provided.
For example, if the version number and release date are not available, the download date can be used.
And the contact name\slash email is an alternative to the location\slash repository.
